Four reasons your build is slow

### 2019-01-16 paper.tex
work on slow compiler section

\subsection{Expensive command}

@@

\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  cc -I../lib -I../lib/common -I../lib/compress -I../lib/dictBuilder 
     -DXXH\_NAMESPACE=ZSTD\_ -I../lib/legacy -DZSTD\_LEGACY\_SUPPORT=5 -O3 
     -DBACKTRACE\_ENABLE=0 
     ../lib/common/debug.c ../lib/common/entropy\_common.c ../lib/common/error\_private.c 
     ../lib/common/fse\_decompress.c ../lib/common/pool.c ../lib/common/threading.c 
     ../lib/common/xxhash.c ../lib/common/zstd\_common.c ../lib/compress/fse\_compress.c 
     ../lib/compress/hist.c ../lib/compress/huf\_compress.c 
     ../lib/compress/zstd\_compress.c ../lib/compress/zstd\_double\_fast.c 
     ../lib/compress/zstd\_fast.c ../lib/compress/zstd\_lazy.c 
     ../lib/compress/zstd\_ldm.c ../lib/compress/zstd\_opt.c 
     ../lib/compress/zstdmt\_compress.c ../lib/decompress/huf\_decompress.c 
     ../lib/decompress/zstd\_decompress.c ../lib/dictBuilder/cover.c 
     ../lib/dictBuilder/divsufsort.c ../lib/dictBuilder/fastcover.c 
     ../lib/dictBuilder/zdict.c ../lib/legacy/zstd\_v05.c ../lib/legacy/zstd\_v06.c 
     ../lib/legacy/zstd\_v07.c zstdcli.o fileio.o bench.o datagen.o dibio.o -o zstd
\end{Verbatim}

@@

\begin{verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
cc -I. -I./common -DXXH_NAMESPACE=ZSTD_ -I./legacy -DZSTD_LEGACY_SUPPORT=5 -O3 common/debug.c common/entropy_common.c common/error_private.c common/fse_decompress.c common/pool.c common/threading.c common/xxhash.c common/zstd_common.c compress/fse_compress.c compress/hist.c compress/huf_compress.c compress/zstd_compress.c compress/zstd_double_fast.c compress/zstd_fast.c compress/zstd_lazy.c compress/zstd_ldm.c compress/zstd_opt.c compress/zstdmt_compress.c decompress/huf_decompress.c decompress/zstd_decompress.c deprecated/zbuff_common.c deprecated/zbuff_compress.c deprecated/zbuff_decompress.c dictBuilder/cover.c dictBuilder/divsufsort.c dictBuilder/fastcover.c dictBuilder/zdict.c legacy/zstd_v05.c legacy/zstd_v06.c legacy/zstd_v07.c -shared -fPIC -fvisibility=hidden -Wl,-soname=libzstd.so.1 -o libzstd.so.1.3.7
\end{verbatim}

@@

>>>>

\subsection{Expensive command}
\label{sec:expensive}

@@

\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  cc \$(FLAGS)
  ../lib/common/debug.c
  ../lib/common/entropy\_common.c
  \textrm{\emph{25 more .c files}}
  zstdcli.o fileio.o bench.o
  datagen.o dibio.o -o zstd
\end{Verbatim}

@@

\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  cc \$(FLAGS)
  common/debug.c
  common/entropy\_common.c
  \textrm{\emph{28 more .c files}}
  -shared -fPIC -fvisibility=hidden
  -Wl,-soname=libzstd.so.1 -o libzstd.so.1.3.7
\end{Verbatim}

@@

A similar issue to the one described in section \ref{sec:expensive} is when a build's
span is dominated by the compilation of a single file.  This problem however cannot be
solved in the makefile like the zstd issue was.  Solutions to this problem include
breaking the file up into smaller files which can be compiled in parallel and then
linked; or changing the compiler so that it is capable of compiling the file faster.
A faster compiler, would have the additional benefit of not only decreasing the span
of the project but also likely decreasing the work of the project.

Google's protocol buffers project \cite{} exhibited this behavior.  It had a relatively
long predicted span of ?? seconds, which was dominated by a call to g++ which was
compiling a single file.  When we apply the same analysis as we applied to zstd in
section \ref{sec:expensive}, we see that if \ref{} wasn't a part of the span, the new
span would be ?? and would be dominated by another g++ compilation of a single file.
And we continue this again to find that the 3 top span paths are dominated by g++
compilations of individual files.  If none of these calls were part of the span, the
new span of the project would be ??.  Now if the developers of protocol buffers were
interested in increasing the parallelism of their project they would know where they
should focus their efforts

Here is a simplification of the real command run by make; it took about 40 seconds to run.
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  g++ \$(FLAGS)
  -o google/protobuf/descriptor.lo
  google/protobuf/descriptor.cc
\end{Verbatim}

Here is a simplification of the real command run by make; it took about 27 seconds to run.
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  g++ \$(FLAGS)
  -o google/protobuf/descriptor.pb.lo
  google/protobuf/descriptor.pb.cc
\end{Verbatim}

Here is a simplification of the real command run by make; it took about 22.5 seconds to run.
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  g++ \$(FLAGS)
  -o google/protobuf/compiler/cpp/cpp\_message.lo
  google/protobuf/compiler/cpp/cpp\_message.cc
\end{Verbatim}

% so, if the problem is with compiling a single file, then we don't really have a
% make level solution to that problem
% user needs to do some work at the file/compiler level to create a solution
% potential solutions include breaking the file up into smaller files which can be
% compiled and linked in paralle
% using a faster compiler, which would have the added benefit of likely decreasing
% the overall work of the build as well as the span
% maybe trying to motivate some future work here

% example project is protobufs c++ version;
% We perform the same analysis that we did in section expensive;
% look at the top spans and what they are dominated by
% we see that the top 3? are dominated by g++ compilations of single files
% and if those are no longer part of the span we half our span; which would result in a
% double speedup
% so we now have a place to focus our energy for improvements
% HIgh level; non make level fix; expensive section is a make level fix; should mention that
% there maybe
